### 2020-05-14 article_draft.tex
More edits

\documentclass{article}
\usepackage[margin = 1in]{geometry}
\usepackage[table]{xcolor}
\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell,natbib, pdfpages}
\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\bibliographystyle{plainnat}

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{refproof}{Proof}
\author{Adam Elder}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sh}{\textcolor{red}}
\newcommand{\pr}{\text{Pr}}
\newcommand{\vmat}{\Sigma}
\newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
\usepackage[mathscr]{euscript}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\definecolor{Gray}{gray}{0.95}
\newcommand{\rvo}{X}
\newcommand{\norm}{f}
\newcommand{\rvoo}{x}
\newcommand{\disto}{P}
\newcommand{\tst}{\hat{\boldsymbol{t}}}
\newcommand{\rvt}{Y}
\newcommand{\rvv}{Z}
\newcommand{\distv}{Q}
\newcommand{\Gammaf}{\Gamma_{\Sigma}}
\newcommand{\Gammafe}{\Gamma_{\hat{\Sigma}}}
\newcommand{\pf}{\Phi}
\newcommand{\gi}{\Upsilon}

\begin{document} 
\doublespacing

\begin{abstract}
It is common across scientific disciplines to be interested in predicting an outcome using some (potentially large) number of covariates.  A first step to constructing accurate predictions is to decide if any covariate is associated with the outcome. Testing for the existence of an association can be done with a variety of existing methods, but frequently a trade off is made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).  We propose an approach testing for the existence of an association between an outcome and any number of covariates that can be carried out for most parameters of interest that performs nearly as well as tests designed for a specific parameter and data generating mechanism.  We compare our method with other modern methods in a simple simulated data setting.  We then study the tests performance in a setting with a complex sampling scheme, and a setting with a complex parameter of interest.  
\end{abstract}

@@

One of the central goals of science is to be able to predict some outcome, often with the help of other related information.  This goal is often attained using the construction of mathematical and statistical models in which many covariates are used to predict the outcome of interest. Because the accuracy of the models is dependent on the presence of an association between the outcome of interest and some number of the covariates it is important to know if any associations exist before attempting to create a model. While this first step is always important, it has become more important as it becomes more common for large numbers of covariates to be collected, often without an explicit outcome of interest in mind.

To test if any covariate is associated with the outcome, a standard approach is to test each covariates association with the outcome. It is desirable for the testing procedure to account for the potentially large number of hypotheses that are simultaneously being tested when using this approach.

Work with \textcolor{red}{simultaneous hypothesis testing}
began with Tukey in 1953 \citep{miller_simultaneous_1981}.  Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.  Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.  Bonferroni-based correction procedures are easy to apply to already existing tests, while guaranteeing family-wise error control. However because these tests ignore the joint distribution of the test statistics, they suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.

Newer procedures \citep{donoho_higher_2004} and \sh{add other papers here} attain improved power compared to Bonferroni-based methods, but often rely on asymptotics to obtain these results, and don't account for the irregularity of the estimator on which their test is based.  Subsequent work \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016} addressed these concerns by accounting for the adaptive nature of the considered tests.  While these tests obtain higher power while maintaining type one error control, they were constructed using assumptions about the data generating mechanism, and for only a single measure of association between the outcome of interest and each covariate.  As a result, investigators may still choose to use bonferroni correction based tests if they are interested in a different measure of association or are unsure of how deviations from the assumed data generating mechanism could effect the properties of the testing procedure.

In this article a testing procedure is proposed that can be used for a wide variety of data generating mechanisms and parameters of interest, but also achieves comparable power to tailor made procedures. Section \ref{sec:Working Examples} describes the data generating mechanisms that are considered to evaluate the performance of the test and the competing test made for the given data generating mechanism.  Section \ref{sec:prop_test_proc} proposes the testing procedure. Section \ref{sec:sim_stdy} shows the performance of our testing procedure in the three considered simulation settings. Section \ref{sec:data_app} shows the application of our method to real world data.  Section \ref{sec:discuss} summarizes the findings of this article and notes potential weaknesses and extensions of our procedure.
%This is done using a two step procedure.  In the first step, the limiting distribution of the entire vector of parameter estimates is estimated.  Next, an adaptive procedure selects a transformation of the vector of parameter estimates and distribution which is guessed provides the best power.  P-values are obtained using a permutation procedure.

\section{Working Examples}
\label{sec:Working Examples}
Let $\rvo_1, \dots, \rvo_n$ be independent identically distributed draws from some distribution $\disto$, and let $\boldsymbol{\rvo} = \{\rvo_1, \dots, \rvo_n\}$ . Let $\rvo_i = \left(Y_i, W_{1 i}, \dots, W_{d i}\right), i \in \{1, \dots n\}$ where $Y$ is the outcome of interest, and each $W$ is a covariate. Let $\psi_1 = \Psi_1(\disto), \dots, \psi_a = \Psi_a(\disto)$ be measures of association between $Y$ and some combination of the $W_j$'s.  While the results found in this article are valid for any integer $a$, for the remainder of this article assume $a = d$, the number of covariates. Also, let $\psi_j$ correspond to a measure of association between $Y$ and $W_j$.  The null hypothesis for our test will be the strong null:

\begin{align*}
H_0: \psi_1 = \psi_2 = \dots = \psi_a = 0 \hspace{0.1cm}\text{  versus  } \hspace{0.1cm} H_1: \psi_j \neq 0 \text{ for some } j \in \{1, \dots, a\}.
\end{align*}

Last, let $\mathscr{M}$ denote the set of all possible distributions, and let $\mathscr{M}_0  \subset \mathscr{M}$ be the subset of distributions in $\mathscr{M}$ satisfying $H_0$.

We consider three different simulated data settings to study the test's performance.

\subsection{Correlation Parameter}
We will compare our method to a Bonferroni correct marginal testing method and the method described in \citep{zhang_comment_2015}.  The settings considered will be the same as the firs setting in \citep{mckeague_adaptive_2015}.  The parameter of interest, $\psi_j(P)$ will be the correlation between the outcome of interest and the $j$'th covariate.

The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$. Three different models for the outcome of interest ($Y$) will be considered. For all considered settings, $\varepsilon \sim N(0, 1)$ and is independent of all $X$. In the first model $Y = \varepsilon$, in the second model $Y = X_1 / 4 + \varepsilon$, and in the third model $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.  Sample sizes of $100$ and $200$, dimensions of $10$, $50$, $100$, $150$, and $200$, and $\rho$ of  $0, 0.5$, and $0.8$ are considered.  All combinations of model, sample size, dimension and $\rho$ are considered, and every test's performance is measured for all considered settings.

\subsection{Missing Data Example}
In the second example, $Y$ is binary, $\Delta$ is a missingness indicator, and each $W_j$ is a covariate of interest.  When $\Delta = 0$ we don't observe $Y$.  The identifying assumption is $\Delta \indep Y | W$, and the parameter of interest is the risk ratio under a poission working model for the probability that $Y = 1$.

\begin{align*}
	\Psi_{j}\left(P^{\text{full}}\right) &= \frac{\text{Cov}\left(\log\left(Pr \left(Y = 1 |  W_j\right)\right), W_j\right)}{\text{Var}(W_j)}.\\
\end{align*}

Using the identifying assumption, the observed data parameter is:

\begin{align*}
	\tilde{\Psi}_{j}\left(P^{\text{obs}}\right)&= \frac{\text{Cov}\left(\log\left(E\left[Pr \left(\Delta  Y = 1 | \Delta = 1, W = W\right) |  W_j\right]\right), W_j\right)}{\text{Var}(W_j)}\\
\end{align*}

The data are drawn from a binomial model:

\begin{align*}
    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta.
\end{align*}

There will be three settings considered which determine  the values of the $\beta$'s in the data generating model:

In all simulation settings the working model is used to take draws from $y$. In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\Sigma_{DE2}$ where $\Sigma_{DE2, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.  $A$ is drawn from a binomial distribution independent from $W$.  For all three settings

\begin{align*}
	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \sum_{i = 1}^{d} \beta_{i} w_i
\end{align*}

In the first setting $\beta_1 \dots \beta_d = 0$.  In the second setting $\beta_1 = 3$ and $\beta_2, \dots \beta_d = 0$.  In the last setting, $\beta_1 \dots \beta_5 = 1$, $\beta_6 \dots \beta_{10} = -1$ and $\beta_{11} \dots \beta_d = 0$.  Data are generated from all three models with every possible combination of sample size ($n = 100$, or $200$), and dimension ($d = 10, 50, 100, 150$, or $200$).

\subsection{Marginal Structural Model}
The third data example is a marginal structural model in which we test if the average treatment effect of a binary treatment $A$ is modified by any covariates $W_j$.  The marginal structural model for each $W_j$ is defined by the working model:

\begin{align*}
\text{logit}\left(Pr(Y^{(a)} = 1 | w)\right) = \beta_0 + \beta_1 a + \beta_2 w_j + \beta_3 w_j a
\end{align*}

in which our parameter of interest is:

\begin{align*}
(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left(\text{logit}\left(Pr(Y^{(a)} = 1 | w\right) - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right)^2 dP(w, a)
\end{align*}

The parameter of interest is $\beta_3^*$, but is worth noting that parameter is different from a usual logistic regression parameter because we are marginalizing over all $w_i$, not just $w_j$.

In all simulation settings the working model is used to take draws from $y$. In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\Sigma_{DE3}$ where $\Sigma_{DE3, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.  $A$ is drawn from a binomial distribution independent from $W$.  For all three settings

\begin{align*}
	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \beta_1 a + \sum_{i = 1}^{d} \beta_{i + 1} w_i + \sum_{j = 1}^d \gamma_{j} w_j a
\end{align*}

In every setting, $\beta_1 = 0.2$, $\beta_2, \dots \beta_{d/2 + 1} = 2/\sqrt{d}$, and $\beta_{d/2 + 1} \dots \beta_{d + 1} = 0$.  In the first (null) setting, $\gamma_{1} \dots \gamma{d} = 0$.  In the second setting, $\gamma_{1} = 3$ and $\gamma_{2} \dots \gamma_{d} = 0$.  In the final setting $\gamma_{1} \dots \beta_{5} = 1, \gamma_{6} \dots \beta_{10} = -1$, and $\gamma_{11} \dots \gamma_{d} = 0$.
Data are generated from all three models with every possible combination of sample size ($n = 100$, or $200$), and dimension ($d = 10, 50, 100, 150$, or $200$).

@@

\section{Proposed Testing Procedure}
\label{sec:prop_test_proc}
For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.  Letting $ \tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$ for any $P_0 \in \mathscr{M}_0$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0.\label{eqn:alpha_rej}
\end{align}
While there are many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure. For simplicity, first consider regions defined using an $\ell_2$ norm:
\begin{align}
	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}. \label{eqn:region}
\end{align}
A region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
\begin{align}
	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}. \label{eqn:ra}
\end{align}
To construct a test using the region defined above, let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$. The test can be defined by 
\begin{align}
\label{eqn:simp_test}
	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha(P_0),
\end{align} 
and the corresponding p-values are defined by $
	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.

@@

\subsection{Adaptive selection of a norm}
In the previous section we showed that a test can be defined with a summarizing function and norm. However, the choice of norm can influence the power of the test. In many scenarios it will not be clear a priori which test will have maximal power for the true alternative. The procedure proposed in this section adaptively selects a norm and it will be shown that this procedure achieves greater power than a test with a fixed norm, while maintaining type 1 error control.

The test defined in \eqref{eqn:simp_test} is a function of three objects; the chosen norm, $\sqrt{n}\hat{\boldsymbol{\psi}}$, and the limiting distribution of  $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$. Note that the limiting distribution of $\hat{t}$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$. Thus potential tests can be defined using the finite dimensional $\Sigma$ matrix rather than the infinite dimension distribution $Q(P)$.

>>>>

\documentclass{article}
\usepackage[margin = 1in]{geometry}
\usepackage[table]{xcolor}
\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell,natbib, pdfpages, url}
\usepackage{lineno}[displaymath, mathlines]
\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\bibliographystyle{plainnat}

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{refproof}{Proof}
\author{Adam Elder}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sh}{\textcolor{red}}
\newcommand{\pr}{\text{Pr}}
\newcommand{\vmat}{\Sigma}
\newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
\usepackage[mathscr]{euscript}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\definecolor{Gray}{gray}{0.95}
\newcommand{\rvo}{X}
\newcommand{\norm}{f}
\newcommand{\rvoo}{x}
\newcommand{\disto}{P}
\newcommand{\tst}{\hat{\boldsymbol{t}}}
\newcommand{\rvt}{Y}
\newcommand{\rvv}{Z}
\newcommand{\nrvs}{Y_\Sigma}
\newcommand{\nrvi}{Y_I}
\newcommand{\distv}{Q}
\newcommand{\Gammaf}{\Gamma_{\Sigma}}
\newcommand{\Gammafe}{\Gamma_{\hat{\Sigma}}}
\newcommand{\pf}{\Phi}
\newcommand{\gi}{\Gamma}
\newcommand{\gamestz}{\Gamma(\hat{\rvv}, \hat{\Sigma})}
\newcommand{\gamestp}{\Gamma(\sqrt{n}\hat{\boldsymbol{\psi}}, \hat{\Sigma})}
\newcommand{\rnp}{\sqrt{n} \hat{\boldsymbol{\psi}}}
\newcommand{\gamp}{\Gamma(\sqrt{n}\boldsymbol{\psi}, \Sigma)}
\newcommand{\gamz}{\Gamma(\rvv, \Sigma)}
\newcounter{conditions}

\begin{document}
\linenumbers
\doublespacing

\begin{abstract}
In many scientific disciplines including genetics, neurology, and vaccine development researchers are often interested in understanding the relationship between an outcome and a large set of covariates.  A first step to investigating such relationships is to screen covariates for an association with the outcome. This screening can be achieved using a variety of methods, from general methods such as those based on Bonferroni adjustment to techniques tailored to a single problem.  Existing general methods that can be applied across a variety of problems frequently have lower power. Tailor-made procedures tend to attain higher power by building their procedures around problem-specific information that makes adaptation to new settings difficult. We propose a general framework to test for the existence of an association between an outcome and any number of covariates in which the estimator is adaptively selected to optimize an estimate of local power. We present theoretical asymptotic guarantees for our test under fixed and local alternatives. We then show numerically that tests created using our framework can perform nearly as well as tailor-made methods.  Finally, we develop tests in two settings in which tailor-made methods are not available. 
\end{abstract}

% utilizes information about the asymptotic distribution of the estimators, but does not place restrictions on the data generating mechanism or the parameter of interest
% frequently a trade off is made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).   that can be carried out for most parameters of interest that.  We compare our method with other modern methods in a simple simulated data setting.

@@

To broaden scientific understanding in a field it is typical to seek an understanding of the relationships between various observations.   It is common for the set of potentially related observations to be quite large while the number of truly related observations is small.  Thus an important first step is to find which variables are truly related to each other.
%To discover these relationships, it is common to construct a mathematical or statistical model in which many covariates are used to predict the outcome of interest. Because the usefulnes of these models is dependent on the presence of an association between the outcome of interest and some number of the covariates, it is important to know if any associations exist before working to create a model.
This initial screening step has become increasingly important as the research collect information on more and more potentially related observations.

One method to check for the existence of such relationships or associations is to test the association of each covariate with the outcome. Because of the many tests this procedure could consider, it is desirable for the testing procedure to account for the potentially large number of hypotheses that are simultaneously being tested when using this approach. Work with \textcolor{red}{simultaneous hypothesis testing}
began with Tukey in 1953 \citep{miller_simultaneous_1981}.  Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.  Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.  Bonferroni-based correction procedures are easy to apply to already existing tests, while guaranteeing family-wise error control. However because these tests ignore the joint distribution of the test statistics, they suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.

Newer procedures \citep{donoho_higher_2004} and \sh{add other papers here} using modern statistical theory to provide asymptotic guarantees for their methods and to account for the correlation between parameter estimates.  However, these methods are made for specific parameters and data generating mechanisms and do not account for the irregularity of the estimator on which their test is based. This irregularity can cause poor performance in scenarios in which the probablility of rejecting the null is far away from the $\alpha$ level of the test and one.  Subsequent work \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016} addressed these concerns by accounting for the flexible nature of these adaptive tests.  However these methods were still created for a specific measure of association and data generating mechanisms in mind. Thus while much has been done to improve the performance of tests in certain settings investigators may still use bonferroni based methods because advanced methods do not exist for their particular situation  As a result, investigators may still choose to use bonferroni correction based tests if they are interested in a different measure of association or are unsure of how deviations from the assumed data generating mechanism could effect the properties of the testing procedure.

In this article we propose a testing procedure that can be used for a wide variety of data generating mechanisms and parameters of interest. This test also achieves comparable power to tailor made procedures in some settings. Section \ref{sec:Working Examples} describes the data generating mechanisms and the corresponding parameters that are considered to evaluate the performance of the test and the competing test.  Section \ref{sec:prop_test_proc} describes the testing procedure.  Section \ref{sec:theorems} provides the theoretical guarantees of the described procedure. Section \ref{sec:sim_stdy} shows the performance of our testing procedure in the three considered simulation settings. Section \ref{sec:data_app} shows the application of our method to real world data.  Section \ref{sec:discuss} summarizes the findings of this article and notes potential weaknesses and extensions of our procedure.

%This is done using a two step procedure.  In the first step, the limiting distribution of the entire vector of parameter estimates is estimated.  Next, an adaptive procedure selects a transformation of the vector of parameter estimates and distribution which is guessed provides the best power.  P-values are obtained using a permutation procedure.

\section{Working Examples}
\label{sec:Working Examples}
Throughout all examples let $\rvo_1, \dots, \rvo_n$ be independent identically distributed draws from some distribution $\disto$, and let $\boldsymbol{\rvo} = \{\rvo_1, \dots, \rvo_n\}$. Let $\rvo_i = \left(Y_i, W_{1 i}, \dots, W_{d i}\right), \ i \in \{1, \dots n\}$ where $Y$ is the outcome of interest, and each $W$ is a covariate. Let $\psi_1 = \Psi_1(\disto), \dots, \psi_a = \Psi_a(\disto)$ be measures of association between $Y$ and some combination of the $W_j$s.  While the results found in this article are valid for any integer $a$, for the remainder of this article assume $a = d$, the number of covariates. Also in this article, let $\psi_j$ correspond to a measure of association between $Y$ and $W_j$.  The null hypothesis for our test will be the strong null: 
\begin{align*}
H_0: \psi_1 = \psi_2 = \dots = \psi_a = 0 \hspace{0.1cm}\text{  versus  } \hspace{0.1cm} H_1: \psi_j \neq 0 \text{ for some } j \in \{1, \dots, a\}.
\end{align*}
Finally, let $\mathscr{M}$ denote the set of all possible distributions, and let $\mathscr{M}_0  \subset \mathscr{M}$ be the subset of distributions in $\mathscr{M}$ satisfying $H_0$. We consider three different simulated data settings to study the performance of the test.

\subsection{Correlation Parameter}
In the first example, our method is compared to a Bonferroni correct marginal testing method and the parametric bootstrap analog of the adaptive resampling test described in \citep{zhang_comment_2015} that built on the adaptive resampling test proposed by \citep{mckeague_adaptive_2015}.  This example uses the same settings as those used in the first example of \citep{mckeague_adaptive_2015}.  The parameter of interest $\psi_j(P)$ is the correlation between the outcome of interest and the $j$'th covariate. The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$. Three different models for the outcome of interest ($Y$) will be considered. For every setting $\varepsilon \sim N(0, 1)$ and is independent of all $W$. In the first setting $Y = \varepsilon$, in the second setting $Y = W_1 / 4 + \varepsilon$, and in the third setting $Y = \sum_{k = 1}^{10} \beta_k W_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.  Sample sizes of $100$ and $200$, dimensions of $10$, $50$, $100$, $150$, and $200$, and correlations $(\rho)$ of  $0, 0.5$, and $0.8$ are considered.  All combinations of model, sample size, dimension and correlation are considered, and the performance of each test is measured for every settings.

\subsection{Missing Data Example}
\label{sec:missing_data}
In the second example $Y$ is binary variable and $\Delta$ is a missingness indicator.  When $\Delta = 0$, $Y$ is not observed. The parameter of interest is the risk ratio under a poission working model for the probability that $Y = 1$.
\begin{align*}
	\Psi_{j}\left(P^{\text{full}}\right) &= \frac{\text{Cov}\left(\log\left(Pr \left(Y = 1 |  W_j\right)\right), W_j\right)}{\text{Var}(W_j)}.
\end{align*}
The identifying assumption is $\Delta \indep Y | W$, and when this assumption holds the corresponding identifiable parameter is:
\begin{align*}
	\tilde{\Psi}_{j}\left(P^{\text{obs}}\right)&= \frac{\text{Cov}\left(\log\left(E\left[Pr \left(\Delta  Y = 1 | \Delta = 1, W = W\right) |  W_j\right]\right), W_j\right)}{\text{Var}(W_j)}.
\end{align*}
The data are drawn from a binomial model:
\begin{align*}
    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta.
\end{align*}
and in all settings, the probability of missingness is given by 
\begin{align*}
% probs <- expit(-0.25 + 1 * ws[, max(1, ncol(ws) - 1)] -
% 1.5 * ws[, max(2, ncol(ws))])
	\text{logit}(\pr(A = 1 | w)) = -0.25 + 1 w_{d - 1} - 1.5 w_d \text{ where d is the number of covariates.} 
\end{align*}

There will be three settings considered which determine  the values of the $\beta$s in the data generating model.  While it is not necessary for the covariates to be normally distributed, in each setting the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\textcolor{blue}{\Sigma_{DE2}}$ where $\Sigma_{DE2, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$. $A$ is drawn from a binomial distribution independent from $W$.  For all three settings 
\begin{align*}
	\text{logit}\left[Pr(Y = 1 | w, a)\right] = \sum_{i = 1}^{d} \beta_{i} w_i
\end{align*}
In the first setting $\beta_1, \dots, \beta_d = 0$.  In the second setting $\beta_1 = 3$ and $\beta_2, \dots,  \beta_d = 0$.  In the last setting, $\beta_1, \dots, \beta_5 = 1$, $\beta_6, \dots, \beta_{10} = -1$ and $\beta_{11}, \dots, \beta_d = 0$.  Data are generated using all three settings with every possible combination of sample size ($n = 5,000$, or $10,000$), and dimension ($d = 10, 50, 100, 150$, or $200$).

\subsection{Marginal Structural Model Example}
\label{sec:msm_data}
The third data example is a marginal structural model in which we test if the average treatment effect of a binary treatment $A$ is modified by any covariates $W_j$.  The marginal structural model for each $W_j$ is defined by the working model:
\begin{align}
\text{logit}\left[Pr(Y^{(a)} = 1 | w)\right] = \beta_0 + \beta_1 a + \beta_2 w_j + \beta_3 w_j a \label{eqn:DE2param}
\end{align}
in which our parameter of interest is:
\begin{align*}
(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left\{\text{logit}\left[Pr\left(Y^{(a)} = 1 | w\right)\right] - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right\}^2 dP(w, a)
\end{align*}
The parameter of interest is $\beta_3^*$, but it is worth noting that this parameter is different from a usual logistic regression parameter because we are marginalizing over all other $w_i$.

In all simulation settings the working model is used to take draws from $Y$. In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\textcolor{blue}{\Sigma_{DE3}}$ where $\Sigma_{DE3, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.  $A$ is drawn from a binomial distribution independent from $W$.  For all three settings

\begin{align*}
	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \alpha a + \sum_{i = 1}^{d} \beta_{i} w_i + \sum_{j = 1}^d \gamma_{j} w_j a
\end{align*}

In every setting, $\alpha = 0.2$, $\beta_1, \dots, \beta_{d/2} = 2/\sqrt{d}$, and $\beta_{d/2}, \dots, \beta_{d}  = 0$.  In the first (null) setting, $\gamma_{1}, \dots, \gamma_{d} = 0$.  In the second setting, $\gamma_{1} = 3$ and $\gamma_{2}, \dots, \gamma_{d} = 0$.  In the final setting $\gamma_{1}, \dots, \gamma_{5} = 0.15$, $\gamma_{6}, \dots, \gamma_{10} = -0.15$, and $\gamma_{11}, \dots, \gamma_{d} = 0$.
Data are generated using all three settings with every possible combination of sample size ($n = 1,000$, or $2,000$), and dimension ($d = 10, 30$, or $75$).

@@

\section{Proposed Testing Procedure}
\label{sec:prop_test_proc}

For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by checking if $\tst$ falls within acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.  Letting $\tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$ for any $P_0 \in \mathscr{M}_0$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
\end{align}
While there are many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure. For simplicity, first consider regions defined using an $\ell_2$ norm:
\begin{align}
	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}. \label{eqn:region}
\end{align}
A region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
\begin{align}
	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}. \label{eqn:ra}
\end{align}
To construct a test using the region defined above, let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Letting $\tst \equiv \sqrt{n}\hat{\boldsymbol{\psi}}$, suppose for now that  $\tst$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$. The test can be defined by 
\begin{align}
\label{eqn:simp_test}
	\text{reject } H_0 \text{ if } \|\rnp\|_2 \geq r_\alpha(P_0),
\end{align} 
and the corresponding p-values are defined by $
	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\rnp\|_2)$.

@@

\subsection{Adaptive selection of a norm}
In the previous section we showed that a test can be defined with a summarizing function and norm. However, the choice of norm can influence the power of the test. In many scenarios it will not be clear a priori which test will have maximal power because the power of each test depends on the unknown value of the true alternative. The procedure proposed in this section data adaptively selects a norm to attain some of the power improvements that can be attained from selecting the best norm without needing to specify the norm a priori. It will be shown via simulation that this procedure can achieve greater power than a test with a fixed norm.  It will also be shown with  both theory and simulation that this adaptive procedure maintains type 1 error control for large sample sizes.

% The test defined in \eqref{eqn:simp_test} is a function of three objects; the chosen norm, $\sqrt{n}\hat{\boldsymbol{\psi}}$, and the limiting distribution of  $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$. Note that the limiting distribution of $\hat{t}$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$. Thus potential tests can be defined using the finite dimensional $\Sigma$ matrix rather than the infinite dimension distribution $Q(P)$.

To define norm data adaptive selection rules it will be important to measure the performance of each test. These measures will be referred to as performance metrics and will be denoted by $\Gamma$. While these metrics can be quite general, they should provide an ordering in which better performance results in a more extreme measure of performance. These metrics should provide reasonable comparisons across norms.  For example if one were to use the $\ell_p$ of the test statistic as the performance metric, the first criteria would be satisfied because for most definitions of ``large'' as $x$ grows large, so does $\|x\|_p$.  However, the second criateria is not satisfied because $\ell_1(x) \geq \ell_2(x) \geq \dots \geq \max(x)$, it does not satisfy the second criteria.

In order to achieve both criteria mentioned previously, the performance metrics considered in this paper will be functions of both the test statistic $\tst$ and the limiting distribution of the test statistic $\rvt$ under the null. The limiting distributions will allow us to understand how extreme $\tst$ is relative to what we would see under the null which allows us to make comparisons across norms.
